%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% % Sections formatting
% \titleformat{\section}{
%   \vspace{-4pt}\scshape\raggedright\large\bfseries
% }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge \scshape Vishwaksena Vishnu Simha Dingari} \\ \vspace{2pt}
  % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
  \href{tel:+918374365916}{\small \raisebox{-0.1\height}\faPhone \ \underline{+91\,837-436-5916}} ~
  \href{https://github.com/vishwaksena-dingari}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/vishwaksena-dingari}}  ~\\ \;\;
  \href{mailto:vishwaksena.dingari@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{vishwaksena.dingari@gmail.com}} ~
  \href{https://www.linkedin.com/in/vishwaksena-dingari-8b2ab9218}{\raisebox{-0.2\height}\faLinkedinIn\ \underline{linkedin.com/in/vishwaksena-dingari-8b2ab9218}}  ~
  \vspace{-8pt}
\end{center}
%---------------------------

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Institute of Technology, Manipur}{2019 -- 2023}
{Bachelor of Technology (B.Tech) in Computer Science and Engineering(\textbf{GPA: 8.63})}{Imphal, Manipur}
\resumeSubHeadingListEnd
%-------------------------------




%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{An OCR System for Meetei-Mayek Script} $|$ \emph{Python, CNN, Transfer Learning}}{July 2023}
\resumeItemListStart
\resumeItem{Developed a robust printed character recognition system for the Meetei-Mayek script of the Manipuri language, involving image preprocessing, segmentation, and database creation.}
\resumeItem{Implemented a comprehensive segmentation approach, initially breaking down text-containing images into lines and subsequently into words through a simplified histogram segmentation method. Further refinement was achieved by utilizing contour-based techniques to extract individual letters from words.}
\resumeItem{Implemented state-of-the-art convolutional neural networks (CNNs), including VGG-16, VGG-19, ResNet152-V2, and MobileNetV2, using transfer learning to achieve an impressive accuracy of approximately 97\% in character classification.} \vspace{-10pt}
% \resumeItem{Contributed to advancing the field of character recognition and language preservation by addressing the unique challenges of Meetei-Mayek script through innovative image processing and deep learning techniques.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{Vidly and Vidly API} $|$ \emph{React, NodeJS, MongoDB}}{April 2022}
\resumeItemListStart
\resumeItem{A Web-Interface and API for a comprehensive movies database.}
\resumeItem{Implemented robust authentication mechanisms and seamlessly integrated the Web-Interface with the API, facilitating essential user actions such as signup, login, logout, and error logging for enhanced system security and user experience.}
\resumeItem{Executed CRUD (Create, Read, Update, Delete) operations, Incorporated advanced features such as filtering, pagination and search, enhancing the user interaction, experience and optimizing data retrieval.}
\resumeItem{Employed JSON Web Tokens (JWTs) to fortify login sessions, ensuring the precise identification of privileged admin users while bolstering the overall security of the system.}
\resumeItemListEnd
\vspace{-13pt}
% \resumeProjectHeading
% {\textbf{Transaction Management GUI} $|$ \emph{Java, Android Studio}}{July 2021}
% \resumeItemListStart
% \resumeItem{}
% \resumeItem{}
% \resumeItem{}
% \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}
%------------------------------




%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{OmniMuse Consultants}{August 2021 -- September 2021}
{Coding Curriculum Development Internship}{Remote}
\resumeItemListStart
\resumeItem{Developed educational modules in HTML, CSS, Javascript, Python, and Java, serving diverse coding backgrounds.}
\resumeItem{Leveraged external libraries like pygames and p5.js to enrich the learning journey, promoting hands-on application.}
\resumeItem{Developed a curriculum that spans from introductory to intermediate levels, ensuring comprehensive skill development.}
\resumeItem{Played a pivotal role in shaping a well-rounded curriculum in HTML, CSS, Javascript, Python, and Java.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}
%--------------------------------




%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{\textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL, PHP} \\
        \textbf{Developer Tools}{: VS Code, Android Studio} \\
        \textbf{Libraries/Technologies/Frameworks}{: GitHub, NodeJS, ReactJS, Bootstrap}
        }
\end{itemize}
\vspace{-16pt}
%----------------------------------------


%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
%\resumeSubHeadingListStart
\begin{multicols}{4}
  \begin{itemize}[itemsep=-5pt, parsep=3pt]
    \item\small Data Structures
    \item Software Methodology
    \item Algorithms
    \item Database Management
    \item Object-Oriented Programming
    \item Machine Learning
    \item Artificial Intelligence
  \end{itemize}
\end{multicols}
\vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd
%--------------------------------


%-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
\section{Achievements}
\resumeSubHeadingListStart
\resumeSubheading{\href{https://link.springer.com/chapter/10.1007/978-981-99-4713-3_50}{An OCR System for Meetei-Mayek script}}{2023}{A Printed Character Recognition System for Meetei-Mayek Script Using Transfer Learning}{ICSTE-23}
\resumeItemListStart
\resumeItem{Published a paper on OCR system for the Meetei-Mayek script of the Manipuri language. The system includes image preprocessing, segmentation, and database creation. Implemented a state-of-the-art convolutional neural network which achieved a high level in character classification.}
% \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
% \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
% \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%-------------------------------------




\end{document}